Descriptive_Stats

### 2023-07-20 Code/RankComparison.Rmd
Added the exact=True argument below the other tests

```{r}
inter <- read.csv("../Data/2019vs2022.csv")

#nine is used for 2019 and two is used for 2022.  H, S, F are used to denote the heats, semifinals, and finals.
colnames(inter) <- c("Athlete", "Country", "2019H", "2019S", "2019F", "2022H", "2022S", "2022F")
```

```{r}
my_sums <- colSums(!is.na(inter))
print(my_sums)
barplot(my_sums)
```

```{r}
means <- sapply(inter[,3:ncol(inter)], mean, na.rm = TRUE)
print(means)

```

```{r}
library(ggplot2)
means_df <- data.frame(variable = names(means), mean = means)

# Define the grouping of bars
groupings <- list(c("2019H", "2022H"), c("2019S", "2022S"), c("2019F", "2022F"))

# Convert variable to a factor with desired order
means_df$variable <- factor(means_df$variable, levels = unlist(groupings))

# Create the bar graph
ggplot(means_df, aes(x = variable, y = mean, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("sienna2", "tan", "sienna2", "tan", "sienna2", "tan")) +
  labs(y = "Mean Reaction Time", x ="") +
  theme_minimal() +
  theme(legend.position = "none")
ggsave(filename="2019vs2022BarGraph.pdf", path = "../Manuscript", height=4, width=6)
```

@@

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, alternative = "greater", method = "ds")
```

>>>>

@@

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, alternative = "greater", method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, alternative = "greater", method = "ds", exact = TRUE)
```

```{r}
comp <- read.csv("../Data/Clusrank2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(comp) <- c("Time", "Athlete", "Year")
#View(comp)
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp, alternative = "greater", method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp, alternative = "greater", method = "ds", exact = TRUE)
```
